<<<<<<< HEAD
---
title: "ESM 204 HW 3"
author: "Jennifer Truong"
date: "5/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

# Attach packages

library(tidyverse)
library(janitor)
library(ggpmisc)
```

## Initial info

```{r initial info}

gas_price = 3.00
envi_externality = 1.50
cc_externality = .50

# Read in data

gas_df <- read_csv("Homework 3 Data.csv") %>% 
  clean_names() %>% 
  mutate(
    aggregate_q = q_low_gallons + q_high_gallons
  )

```

## Question 1 

#### Finding Supply and Demand Curves

```{r individual demand curves}

# Low income -----

# Find demand curve for low income
ggplot(gas_df, aes(x = q_low_gallons, y = price_dollars)) +
  geom_point() +
  geom_smooth(method = "lm",
              se = FALSE,
              formula = y ~ x) +
    stat_poly_eq(parse = T,
               aes(label = ..eq.label..),
               formula = y ~ x)

# Equation for low income demand curve
demand_low = function(q){p = 11.7 - (6.61*10^(-5))*q} 

# For low demand curve at P = 0, Q = 177004.538577912

# 0 = 11.7 - 6.61*10^(-5)*q_low
# -11.7 = -6.61*10^(-5)*q_low
q_low = -11.7/(-6.61*10^(-5))

# High income ----

# Find demand curve for high income
ggplot(gas_df, aes(x = q_high_gallons, y = price_dollars)) +
  geom_point() +
  geom_smooth(method = "lm",
              se = FALSE,
              formula = y ~ x) +
    stat_poly_eq(parse = T,
               aes(label = ..eq.label..),
               formula = y ~ x)

# Equation for high income demand curve
demand_high = function(q){p = 15.8 - (2.73*10^(-5))*q} 

# For high demand curve at P = 0, Q = 177004.538577912

# 0 = 15.8 - 2.73*10^(-5)*q_high
# -15.8 = -2.73*10^(-5)*q_high
q_high = -15.8/(-2.73*10^(-5))

```


Low income demand curve: $P = 11.7 - (6.61*10^{-5})Q$

High income demand curve: $P = 15.8 - (2.73*10^{-5})Q$

```{r aggregate demand curve}
# Find aggregate demand curve ----

# Graph aggregate demand curve
ggplot(gas_df, aes(x = aggregate_q, y = price_dollars)) +
  geom_point() +
  geom_smooth(method = "lm",
              se = FALSE,
              formula = y ~ x) +
    stat_poly_eq(parse = T,
               aes(label = ..eq.label..),
               formula = y ~ x)

# Equation for high income demand curve
demand_agg = function(q){p = 15 - (2.04*10^(-5))*q}

# For aggregate demand curve at P = 0, Q = 735294.117647059

# 0 = 15 - 2.04*10^(-5)*q_low
# -15 = -2.04*10^(-5)*q_low
q_agg = -15/(-2.04*10^(-5))
```

Aggregate demand curve: $P = 15 - (2.04*10^{-5})Q$

Supply curve: $P = 5.110*10^{-6}Q$

```{r Graphing all demand curves with supply curve}
# Supply Curve -------

# The marginal cost of producing a gallon of gasoline is linear and has price-intercept of 0.

# For current price to be 3, the supply curve must intersect the aggregate demand curve at P = 3.

# Finding market equilibrium ----

# Set supply and aggregate demand curves equal to each other to find Q
# 3 = 15 - (2.04*10^-5)Q
# -12 = -2.04*10^(-5)Q
q_equil = -12/(-2.04*10^(-5))

supply_slope = (3-0)/(q_equil - 0)

supply_curve = function(q){p = supply_slope*q}

# Supply curve equation = 5.1e-06x

# Supply and Demand Plot ----

gas_plot = ggplot(data = gas_df, mapping = aes(x = aggregate_q,
                                    y = price_dollars)) +
  stat_function(fun = demand_low,
                aes(color = "demand_low")) +
  stat_function(fun = demand_high,
                aes(color = "demand_high")) +
  stat_function(fun = demand_agg,
                aes(color = "demand_agg"),
                size = 1.5) +
  stat_function(fun = supply_curve,
                aes(color = "supply_curve"),
                size = 1.5) + # Supply curve
  geom_hline(yintercept=0, color="black") + # Emphasize y-axis
  geom_vline(xintercept=0, color="black") + # Emphasize x-axis
  expand_limits(x=c(0,750000), y=c(0, 15))

gas_plot

```

At market equilibrium, the price is `r gas_price` dollars and the quantity is `r q_equil` gallons. 

####  Finding benefits

```{r Benefits}
# Consumer Benefit ---

cs_agg = 0.5*(15-3)*q_equil

# Producer Benefit ---

ps_statquo = 0.5*3*q_equil

```

- The benefit to consumers under the status quo is `r cs_agg`
- The benefit to producers under the status quo is `r ps_statquo`

#### Envi Cost

```{r}
# Graph with MEC ----

gas_mec_graph = gas_plot + 
  geom_hline(yintercept=1.5, color="brown", size=0.7) # MEC curve

gas_mec_graph

# Finding Envi Cost Locally ----

envi_cost_gas = envi_externality*q_equil
envi_cost_gas_global = cc_externality*q_equil
```

The local environmental cost under the status quo is $`r envi_cost_gas`

The global environmental cost under the status quo is $`r envi_cost_gas_global`

## Question 2

#### Individual CS for both Low Income and High Income

```{r Low Income CS}

# Find Q at equilbrium -----

# 3 = 11.7 - 6.61*10^(-5)*q_low
# (3-11.7) = - 6.61*10^(-5)*q_low

q_low_cs = (3-11.7)/(- 6.61*10^(-5))
  
# Low Income CS ------

cs_low = 0.5*(11.7-3)*q_low_cs

```

The consumer benefit for low income is `r cs_low`

```{r High Income CS}

# Find Q at equilbrium -----

# 3 = 15.8 - 2.73*10^(-5)*q_high
# (3-15.8) = -2.73*10^(-5)*q_high

q_high_cs = (3-15.8)/(-2.73*10^(-5))
  
# High Income CS ------

cs_high = 0.5*(15.8-3)*q_high_cs

```

The consumer benefit for high income is `r cs_high`

## Question 3

#### a) Effect on amount of gas produced and consumed

Supply curve after the tax: $P = (5.110*10^{-6})Q + 1.00$

```{r Equilibrium shift after tax}

# Find new supply curve after tax - just add 1 to y-intercept?

supply_curve_tax = function(q){p = supply_slope*q + 1.00}

# Find equilibrium after tax  ----

# Set supply and aggregate demand curves equal to each other to find Q
# (5.110*10^-6)Q + 1 = 15 - (2.04*10^-5)Q
# (5.110*10^-6)Q + (2.04*10^-5)Q = 14
q_equil_tax = 14/((5.110*10^-6) + (2.04*10^-5))

```

It would reduce the equilibrium quantity to `r q_equil_tax` gallons, down by `r round(100-(q_equil_tax/q_equil*100), 2)`%.

#### b) Price on gas

```{r Gas Price after tax}

gas_price_tax = gas_price + 1

```


It would increase the curent price from 3 to `r gas_price_tax` dollars.

#### c) Welfare of “High” income consumers.

```{r High Income CS after Tax}

# Find new Q for equil for high income after tax

# 4 = 15.8 - 2.73*10^(-5)*q_high_tax
# (4-15.8) = -2.73*10^(-5)*q_high_tax

q_high_tax = (4-15.8)/(-2.73*10^(-5))

# Plug in 4 as the new equil price and __ as the new equil quantity

cs_high_tax = 0.5*(15.8-4)*q_high_tax
```

The tax would reduce the welfare of high income customers to `r cs_high_tax`, down by `r round(100-(cs_high_tax/cs_high*100), 2)`%.

#### d) Welfare of “Low” income consumers.

```{r Low Income CS after Tax}

# Find new Q for equil for low income after tax

# 4 = 11.7 - 6.61*10^(-5)*q_low_tax - plug in 4 for P
# 4-11.7 = -6.61*10^(-5)*q_low_tax

q_low_tax = (4-11.7)/(-6.61*10^(-5))

# Plug in 4 as the new equil price and __ as the new equil quantity

cs_low_tax = 0.5*(11.7-4)*q_low_tax
```

The tax would reduce the welfare of low income customers to `r cs_low_tax`, down by `r round(100-(cs_low_tax/cs_low*100), 2)`%.

#### e) Welfare of gas producers.

```{r PS after tax}

# Find Q on original supply curve at P = 1

# 1 = 5.110*10^(-6)*q_prod_tax
q_prod_tax = 1/(5.110*10^(-6))

# Find PS after tax

ps_tax = 0.5*1*q_prod_tax

```

The tax would reduce the welfare of high income customers to `r ps_tax`, down by `r round(100-(ps_tax/ps_statquo*100), 2)`%.

#### f) Local environmental damage.

```{r Local Externality after Tax}

# Subtract $1.00 from the local externality of $1.50

```

$1.50 - 1.00 = 0.50$

The tax would cover two thirds of the original local externality of 1.50, leaving $0.50 behind. 

#### g) Rest of world environmental damage.

```{r Global Externality after Tax}

# Subtract $1.00 from the global climate change externality of $0.50

```

$0.50 - 1.00 = -0.50$

The tax would cover the whole climate change externality.

#### h) Total revenue generated by the tax.

```{r Tax revenue}

# Find the difference in P (4-1) multiply by q_equil_tax to get tax revenue

tax_revenue = (gas_price_tax - gas_price)*q_equil_tax
```

The total revenue generated by the tax would be $`r tax_revenue`

## Question 4

#### a) Overall welfare of “High” income consumers
#### b) Overall welfare of “Low” income consumers
#### c) Gas producers

## Question 5 - Electric Vehicle

```{r New Demand Curves with Electric Vehicles}

# Low income demand curve: P = 11.7 - (6.61*10^{-5})Q
# New low income curve:
demand_low_ev = function(q){(11.7 - (6.61*10^{-5})*q)/2}

# High income demand curve: P = 15.8 - (2.73*10^{-5})
# New high income curve:
demand_high_ev = function(p, q){p = (15.8 - (2.73*10^{-5})*q)/2}

```

#### a) Gas consumption by “High” income consumers

```{r Gas Consumption by High Income w/ EV}

# Calculate Q with new demand curve with P at 3

# 3 = (15.8 - (2.73*10^{-5})*q_high_ev)/2
q_high_ev = (6 - 15.8)/(-2.73*10^{-5})

```

The gas consumption by the high income consumers would decrease to `r q_high_ev` gallons, down by `r round(100-(q_high_ev/q_high*100), 2)`%

#### b) Gas consumption by “Low” income consumers

```{r Gas Consumption by Low Income w/ EV}

# Calculate Q with new demand curve with P at 3

# 3 = (11.7 - (6.61*10^{-5})*q_low_ev))/2
q_low_ev = (6 - 11.7)/(-6.61*10^{-5})

```

The gas consumption by the low income consumers would decrease to `r q_low_ev` gallons, down by `r round(100-(q_low_ev/q_low*100), 2)`%

#### c) Gas price

```{r}

# Find new aggregate demand curve ----

# Reduce original aggregate demand curve by half
# p = (15 - (2.04*10^(-5))*q_agg_ev)/2
demand_agg_ev = function(q){(15 - (2.04*10^(-5))*q)/2}

# Find a Q for new equilibrium ----

# Set new aggregate demand curve equal to original supply curve
# (15 - (2.04*10^(-5))*q_agg_ev)/2 = (5.110*10^(-6))*q_agg_ev
# (15 - (2.04*10^(-5))*q_agg_ev) = 2(5.110*10^(-6))*q_agg_ev
# 15 = 2(5.110*10^(-6))*q_agg_ev + (2.04*10^(-5))*q_agg_ev
q_equil_ev = 15/(2*(5.110*10^(-6)) + (2.04*10^(-5)))

# Find the new P for new equilibrum
p_equil_ev = demand_agg_ev(q_equil_ev)

```

The gas price decreases to $`r round(p_equil_ev, 2)`, down by `r round(100-(p_equil_ev/gas_price*100), 2)`%

#### d) Local environmental damage from gasoline

```{r Local externality after EV}

envi_cost_gas_ev = envi_externality*q_equil_ev

```

The local environmental cost with EV implementation is $`r envi_cost_gas_ev`

#### e) Rest of world environmental damage from gasoline

```{r Global Externality after EV}

envi_cost_gas_global_ev = cc_externality*q_equil_ev

```

The global environmental cost with EV implementation is $`r envi_cost_gas_global_ev`

## Question 6

```{r Existing tax revenue under EV}

# Find tax revenue with EV
tax_revenue_ev = (gas_price - p_equil_ev)*q_equil_ev
```
 
=======
---
title: "ESM 204 HW 3"
author: "Jennifer Truong"
date: "5/8/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

# Attach packages

library(tidyverse)
library(janitor)
library(ggpmisc)
```

## Initial info

```{r initial info}

gas_price = 3.00
envi_externality = 1.50
cc_externality = .50

# Read in data

gas_df <- read_csv("Homework 3 Data.csv") %>% 
  clean_names() %>% 
  mutate(
    aggregate_q = q_low_gallons + q_high_gallons
  )

```

## Question 1 

#### Finding Supply and Demand Curves

```{r individual demand curves}

# Low income -----

# Find demand curve for low income
ggplot(gas_df, aes(x = q_low_gallons, y = price_dollars)) +
  geom_point() +
  geom_smooth(method = "lm",
              se = FALSE,
              formula = y ~ x) +
    stat_poly_eq(parse = T,
               aes(label = ..eq.label..),
               formula = y ~ x)

# Equation for low income demand curve
demand_low = function(q){p = 11.7 - (6.61*10^(-5))*q} 

# For low demand curve at P = 0, Q = 177004.538577912

# 0 = 11.7 - 6.61*10^(-5)*q_low
# -11.7 = -6.61*10^(-5)*q_low
q_low = -11.7/(-6.61*10^(-5))

# High income ----

# Find demand curve for high income
ggplot(gas_df, aes(x = q_high_gallons, y = price_dollars)) +
  geom_point() +
  geom_smooth(method = "lm",
              se = FALSE,
              formula = y ~ x) +
    stat_poly_eq(parse = T,
               aes(label = ..eq.label..),
               formula = y ~ x)

# Equation for high income demand curve
demand_high = function(q){p = 15.8 - (2.73*10^(-5))*q} 

# For high demand curve at P = 0, Q = 177004.538577912

# 0 = 15.8 - 2.73*10^(-5)*q_high
# -15.8 = -2.73*10^(-5)*q_high
q_high = -15.8/(-2.73*10^(-5))

```


Low income demand curve: $P = 11.7 - (6.61*10^{-5})Q$

High income demand curve: $P = 15.8 - (2.73*10^{-5})Q$

```{r aggregate demand curve}
# Find aggregate demand curve ----

# Graph aggregate demand curve
ggplot(gas_df, aes(x = aggregate_q, y = price_dollars)) +
  geom_point() +
  geom_smooth(method = "lm",
              se = FALSE,
              formula = y ~ x) +
    stat_poly_eq(parse = T,
               aes(label = ..eq.label..),
               formula = y ~ x)

# Equation for high income demand curve
demand_agg = function(q){p = 15 - (2.04*10^(-5))*q}

# For aggregate demand curve at P = 0, Q = 735294.117647059

# 0 = 15 - 2.04*10^(-5)*q_low
# -15 = -2.04*10^(-5)*q_low
q_agg = -15/(-2.04*10^(-5))
```

Aggregate demand curve: $P = 15 - (2.04*10^{-5})Q$

Supply curve: $P = 5.110*10^{-6}Q$

```{r Graphing all demand curves with supply curve}
# Supply Curve -------

# The marginal cost of producing a gallon of gasoline is linear and has price-intercept of 0.

# For current price to be 3, the supply curve must intersect the aggregate demand curve at P = 3.

# Finding market equilibrium ----

# Set supply and aggregate demand curves equal to each other to find Q
# 3 = 15 - (2.04*10^-5)Q
# -12 = -2.04*10^(-5)Q
q_equil = -12/(-2.04*10^(-5))

supply_slope = (3-0)/(q_equil - 0)

supply_curve = function(q){p = supply_slope*q}

# Supply curve equation = 5.1e-06x

# Supply and Demand Plot ----

gas_plot = ggplot(data = gas_df, mapping = aes(x = aggregate_q,
                                    y = price_dollars)) +
  stat_function(fun = demand_low,
                aes(color = "demand_low")) +
  stat_function(fun = demand_high,
                aes(color = "demand_high")) +
  stat_function(fun = demand_agg,
                aes(color = "demand_agg"),
                size = 1.5) +
  stat_function(fun = supply_curve,
                aes(color = "supply_curve"),
                size = 1.5) + # Supply curve
  geom_hline(yintercept=0, color="black") + # Emphasize y-axis
  geom_vline(xintercept=0, color="black") + # Emphasize x-axis
  expand_limits(x=c(0,750000), y=c(0, 15))

gas_plot

```

At market equilibrium, the price is `r gas_price` dollars and the quantity is `r q_equil` gallons. 

####  Finding benefits

```{r Benefits}
# Consumer Benefit ---

cs_agg = 0.5*(15-3)*q_equil

# Producer Benefit ---

ps_statquo = 0.5*3*q_equil

```

- The benefit to consumers under the status quo is `r cs_agg`
- The benefit to producers under the status quo is `r ps_statquo`

#### Envi Cost

```{r}
# Graph with MEC ----

gas_mec_graph = gas_plot + 
  geom_hline(yintercept=1.5, color="brown", size=0.7) # MEC curve

gas_mec_graph

# Finding Envi Cost Locally ----

envi_cost_gas = envi_externality*q_equil
envi_cost_gas_global = cc_externality*q_equil
```

The local environmental cost under the status quo is $`r envi_cost_gas`

The global environmental cost under the status quo is $`r envi_cost_gas_global`

## Question 2

#### Individual CS for both Low Income and High Income

```{r Low Income CS}

# Find Q at equilbrium -----

# 3 = 11.7 - 6.61*10^(-5)*q_low
# (3-11.7) = - 6.61*10^(-5)*q_low

q_low_cs = (3-11.7)/(- 6.61*10^(-5))
  
# Low Income CS ------

cs_low = 0.5*(11.7-3)*q_low_cs

```

The consumer benefit for low income is `r cs_low`

```{r High Income CS}

# Find Q at equilbrium -----

# 3 = 15.8 - 2.73*10^(-5)*q_high
# (3-15.8) = -2.73*10^(-5)*q_high

q_high_cs = (3-15.8)/(-2.73*10^(-5))
  
# High Income CS ------

cs_high = 0.5*(15.8-3)*q_high_cs

```

The consumer benefit for high income is `r cs_high`

## Question 3

#### a) Effect on amount of gas produced and consumed

Supply curve after the tax: $P = (5.110*10^{-6})Q + 1.00$

```{r Equilibrium shift after tax}

# Find new supply curve after tax - just add 1 to y-intercept?

supply_curve_tax = function(q){p = supply_slope*q + 1.00}

# Find equilibrium after tax  ----

# Set supply and aggregate demand curves equal to each other to find Q
# (5.110*10^-6)Q + 1 = 15 - (2.04*10^-5)Q
# (5.110*10^-6)Q + (2.04*10^-5)Q = 14
q_equil_tax = 14/((5.110*10^-6) + (2.04*10^-5))

```

It would reduce the equilibrium quantity to `r q_equil_tax` gallons, down by `r round(100-(q_equil_tax/q_equil*100), 2)`%.

#### b) Price on gas

```{r Gas Price after tax}

gas_price_tax = gas_price + 1

```


It would increase the curent price from 3 to `r gas_price_tax` dollars.

#### c) Welfare of “High” income consumers.

```{r High Income CS after Tax}

# Find new Q for equil for high income after tax

# 4 = 15.8 - 2.73*10^(-5)*q_high_tax
# (4-15.8) = -2.73*10^(-5)*q_high_tax

q_high_tax = (4-15.8)/(-2.73*10^(-5))

# Plug in 4 as the new equil price and __ as the new equil quantity

cs_high_tax = 0.5*(15.8-4)*q_high_tax
```

The tax would reduce the welfare of high income customers to `r cs_high_tax`, down by `r round(100-(cs_high_tax/cs_high*100), 2)`%.

#### d) Welfare of “Low” income consumers.

```{r Low Income CS after Tax}

# Find new Q for equil for low income after tax

# 4 = 11.7 - 6.61*10^(-5)*q_low_tax - plug in 4 for P
# 4-11.7 = -6.61*10^(-5)*q_low_tax

q_low_tax = (4-11.7)/(-6.61*10^(-5))

# Plug in 4 as the new equil price and __ as the new equil quantity

cs_low_tax = 0.5*(11.7-4)*q_low_tax
```

The tax would reduce the welfare of low income customers to `r cs_low_tax`, down by `r round(100-(cs_low_tax/cs_low*100), 2)`%.

#### e) Welfare of gas producers.

```{r PS after tax}

# Find Q on original supply curve at P = 1

# 1 = 5.110*10^(-6)*q_prod_tax
q_prod_tax = 1/(5.110*10^(-6))

# Find PS after tax

ps_tax = 0.5*1*q_prod_tax

```

The tax would reduce the welfare of high income customers to `r ps_tax`, down by `r round(100-(ps_tax/ps_statquo*100), 2)`%.

#### f) Local environmental damage.

```{r Local Externality after Tax}

# Subtract $1.00 from the local externality of $1.50

```

$1.50 - 1.00 = 0.50$

The tax would cover two thirds of the original local externality of 1.50, leaving $0.50 behind. 

#### g) Rest of world environmental damage.

```{r Global Externality after Tax}

# Subtract $1.00 from the global climate change externality of $0.50

```

$0.50 - 1.00 = -0.50$

The tax would cover the whole climate change externality.

#### h) Total revenue generated by the tax.

```{r Tax revenue}

# Find the difference in P (4-1) multiply by q_equil_tax to get tax revenue

tax_revenue = (gas_price_tax - gas_price)*q_equil_tax
```

The total revenue generated by the tax would be $`r tax_revenue`

## Question 4

#### a) Overall welfare of “High” income consumers
#### b) Overall welfare of “Low” income consumers
#### c) Gas producers

## Question 5 - Electric Vehicle

```{r New Demand Curves with Electric Vehicles}

# Low income demand curve: P = 11.7 - (6.61*10^{-5})Q
# New low income curve:
demand_low_ev = function(q){(11.7 - (6.61*10^{-5})*q)/2}

# High income demand curve: P = 15.8 - (2.73*10^{-5})
# New high income curve:
demand_high_ev = function(p, q){p = (15.8 - (2.73*10^{-5})*q)/2}

```

#### a) Gas consumption by “High” income consumers

```{r Gas Consumption by High Income w/ EV}

# Calculate Q with new demand curve with P at 3

# 3 = (15.8 - (2.73*10^{-5})*q_high_ev)/2
q_high_ev = (6 - 15.8)/(-2.73*10^{-5})

```

The gas consumption by the high income consumers would decrease to `r q_high_ev` gallons, down by `r round(100-(q_high_ev/q_high*100), 2)`%

#### b) Gas consumption by “Low” income consumers

```{r Gas Consumption by Low Income w/ EV}

# Calculate Q with new demand curve with P at 3

# 3 = (11.7 - (6.61*10^{-5})*q_low_ev))/2
q_low_ev = (6 - 11.7)/(-6.61*10^{-5})

```

The gas consumption by the low income consumers would decrease to `r q_low_ev` gallons, down by `r round(100-(q_low_ev/q_low*100), 2)`%

#### c) Gas price

```{r}

# Find new aggregate demand curve ----

# Reduce original aggregate demand curve by half
# p = (15 - (2.04*10^(-5))*q_agg_ev)/2
demand_agg_ev = function(q){(15 - (2.04*10^(-5))*q)/2}

# Find a Q for new equilibrium ----

# Set new aggregate demand curve equal to original supply curve
# (15 - (2.04*10^(-5))*q_agg_ev)/2 = (5.110*10^(-6))*q_agg_ev
# (15 - (2.04*10^(-5))*q_agg_ev) = 2(5.110*10^(-6))*q_agg_ev
# 15 = 2(5.110*10^(-6))*q_agg_ev + (2.04*10^(-5))*q_agg_ev
q_equil_ev = 15/(2*(5.110*10^(-6)) + (2.04*10^(-5)))

# Find the new P for new equilibrum
p_equil_ev = demand_agg_ev(q_equil_ev)

```

The gas price decreases to $`r round(p_equil_ev, 2)`, down by `r round(100-(p_equil_ev/gas_price*100), 2)`%

#### d) Local environmental damage from gasoline

```{r Local externality after EV}

envi_cost_gas_ev = envi_externality*q_equil_ev

```

The local environmental cost with EV implementation is $`r envi_cost_gas_ev`

#### e) Rest of world environmental damage from gasoline

```{r Global Externality after EV}

envi_cost_gas_global_ev = cc_externality*q_equil_ev

```

The global environmental cost with EV implementation is $`r envi_cost_gas_global_ev`

## Question 6

```{r Existing tax revenue under EV}

# Find tax revenue with EV
tax_revenue_ev = (gas_price - p_equil_ev)*q_equil_ev
```
 
>>>>>>> be4b5bc4ac359d1f4e17917bacce46427f3bfe3a
The tax revenue with the gas tax is $`r tax_revenue`, while the tax revenue with the electric car technology and without the tax  is `r tax_revenue_ev`.