---
title: "ESM 204 HW 3 Appendix"
author: "Jennifer Truong, Haley Grant, and Qusai B."
date: "5/8/2020"
output: pdf_document
---

OKAY GITHUB HOPE YOU GET THIS

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)

# Attach packages

library(tidyverse)
library(janitor)
library(ggpmisc)
```


```{r initial info}

gas_price = 3.00
local_externality = 1.50
row_externality = .50

# Read in data ----

# Data frame w/ aggregate quantity for column
gas_df <- read_csv("Homework 3 Data.csv") %>% 
  clean_names() %>% 
  # Add new column for aggregate demand
  mutate(
    q_aggregate = q_low_gallons + q_high_gallons
  )

# Data frame for calculating regression models
gas_df_2 <- gas_df %>% 
  # Use pivot_longer to condense data frame for easier graphing
  pivot_longer(-price_dollars, names_to = 'type', values_to = 'gallons')

```

## Question 1

```{r Low Income Demand Curve, results = "hide"}

# Create linear regression model for low income demand curve
lm_daily_low <- lm(price_dollars~q_low_gallons, data = gas_df)

# Get summary of model outputs to pull values from table
summary(lm_daily_low)
# summary(lm_daily_low)$coefficients[1,1] - gets y-intercept of equation
# summary(lm_daily_low)$coefficients[2,1] - gets slope of equation

# Save into variables
demand_low_y = summary(lm_daily_low)$coefficients[1,1]
demand_low_slope = summary(lm_daily_low)$coefficients[2,1]

# Create function for low income demand curve
demand_low = function(x){y = 11.68548 - (6.611437*10^(-05))*x}

# Low income demand curve: y = 11.68548 - 6.611437e-05x

```

```{r High Income Demand Curve, results = "hide"}

# Create linear regression model for high income demand curve
lm_daily_high <- lm(price_dollars~q_high_gallons, data = gas_df)

# Get summary of model outputs to pull values from table
summary(lm_daily_high)
# summary(lm_daily_high)$coefficients[1,1] - gets y-intercept of equation
# summary(lm_daily_high)$coefficients[2,1] - gets slope of equation

# Save into variables
demand_high_y = summary(lm_daily_high)$coefficients[1,1]
demand_high_slope = summary(lm_daily_high)$coefficients[2,1]

# Create function for low income demand curve
demand_high = function(x){y = 15.80343 - (2.730926*10^(-05))*x}

# High income demand curve: y = 15.80343 - 2.730926e-05x 
```

**‘Low’ income demand curve:** y = `r summary(lm_daily_low)$coefficients[1,1]` - `r summary(lm_daily_low)$coefficients[2,1]`x

**‘High’ income demand curve:** y = `r summary(lm_daily_high)$coefficients[1,1]` - `r summary(lm_daily_low)$coefficients[2,1]`x

```{r Aggregate demand curve}

# Calculate co-efficients
demand_agg_y = 755430.3/51742.92
demand_agg_slope = -1/51742.92

# Create function
demand_agg = function(x){y = 14.59968 - (1.932632*10^(-05))*x}

# Aggregate demand curve: y = 14.59968 - 1.932632e^{-05}x
```

$y_{low} = 11.68548 - 6.611437e-05x_{low}$
$x_{low} = (11.68548/6.611437e-05) + (1/-6.611437e-05)y_{low}$
$x_{low} = 176746.4 - 15125.3y_{low}$

$y_{high} = 15.80343 - 2.730926e-05x_{high}$ 
$x_{high} = (15.80343/2.730926e-05) + (1/-2.730926e-05)y_{high}$
$x_{high} = 578683.9 - 36617.62y_{high}$

$x_{agg} = (176746.4 + 578683.9) + ((1/-6.611437e-05)+(1/-2.730926e-05))$
$x_{agg} = 755430.3 - 51742.92y$

**Aggregate demand curve:** $y_{agg}$ = `r demand_agg_y` - `r demand_agg_slope`$x_{agg}$

```{r Finding Market Equilibirum Quantity}
# Set supply and aggregate demand curves equal to each other to find Q

# 3 = 14.59968 - 1.932632e-05q
q_equil = (gas_price - demand_agg_y)/demand_agg_slope
```

```{r Supply Curve}

# To calculate supply curve, assume the following:
#  - price intercept of 0 (y-intercept = 0)
#  - linear
#  - must intersect the aggregate demand curve at y = 3

supply_slope = (3-0)/(q_equil - 0)

supply_slope_2 = 1/200067

supply_curve = function(gallons){price_dollars = supply_slope*gallons}
```

**Supply curve:** $y = (1/200,067)x$

```{r Supply and Demand Graph}
# Individual Demand Curves ---

gas_demand_plot = ggplot(data = gas_df_2, aes(x = gallons, y = price_dollars, color = type)) +
  geom_point(show.legend = FALSE) +
  geom_smooth(method = 'lm', se = FALSE, size = 0.5, show.legend = TRUE) +
  labs(x = 'gallons',
       y = 'price',
       title = '') +
  theme_light()

# Supply and Demand Plot ----

gas_snd_plot = ggplot(data = gas_df_2, aes(x = gallons, y = price_dollars)) +
  # Demand curves
  stat_function(fun = demand_low,
                aes(color = "demand_low")) +
  stat_function(fun = demand_high,
                aes(color = "demand_high")) +
  # Aggregate demand curve
  stat_function(fun = demand_agg,
                aes(color = "demand_agg"),
                size = 1.5) +
  # Supply curve
  stat_function(fun = supply_curve,
                aes(color = "supply_curve"),
                size = 1.5) + 
  # Local externality
  geom_hline(yintercept = local_externality, color = "red", show.legend = TRUE) +
  # Rest of world (ROW) externality)
  geom_hline(yintercept = row_externality, color = "blue", show.legend = TRUE) +
  geom_hline(yintercept=0, color="black") + # Emphasize y-axis
  geom_vline(xintercept=0, color="black") + # Emphasize x-axis
  ylim(-3,15)

gas_snd_plot

```

#### Consumer Benefit

The benefit to consumers under the status quo is the consumer surplus (the area under the demand curve, which we integrate when the price is $`r gas_price`).

$`r gas_price` = `r demand_agg_y` - `r demand_agg_slope`x

x = `r q_equil` gallons

```{r Finding Consumer Benefit}

# Haley's math ---
#area under the curve = 5,284,660

# Find area under the demand curve

# Find the total cost of gas
gas_total_cost = gas_price*q_equil

# Subtract total cost from whole area under curve



```


`r gas_total_cost` = `r gas_price`*`r q_equil`

5,284,660 - `r gas_total_cost` = 3,484,057

The consumer benefit is $___.

#### Producer Benefit

```{r Finding Producer Benefit}

# Haley's math ---
#  - area under supply curve when price = $3 for consumers
#  - integrate y = 1.932632e-05x from 0 to 600201
# area under the curve = 3,481,070
```

The benefit to producers under the status quo is the producer surplus (the area under the demand curve, which we integrate when the price is $`r gas_price`).

The producer benefit is $___.

#### Environmental Cost

```{r Environmental Costs}

# Local ---

local_ec = local_externality*q_equil

# Rest of world ---

row_ec = row_externality*q_equil
```

##### Local

The local environmental cost is `r local_ec`. It is the area under the curve from 0 to 600201, so we integrate $y = 1.50$ from 0 to 600201

##### Rest of the world

The rest of the world environmental cost is `r row_ec`. It is the area under the curve from 0 to 600201, so we integrate $y = 0.50$ from 0 to 600201

## Question 2 - Individual Consumer Benefit

#### Low Income

```{r Low Income CS}

# Find Q at equilbrium -----

# 3 = 11.7 - 6.61*10^(-5)*q_low
# (3-11.7) = - 6.61*10^(-5)*q_low

q_low_cs = (gas_price - demand_low_y)/demand_low_slope
  
# Low Income CS ------

cs_low = 0.5*(demand_low_y - gas_price)*q_low_cs

```

$x_{low}$ = (`r gas_price` - `r demand_low_y`)/`r demand_low_slope`

The quantity for the low income demand curve where the price is $`r gas_price` is `r q_low_cs`. The consumer surplus is the area of a triangle.
  
`r cs_low` = 0.5 * (`r demand_low_y` - `r gas_price`) *`r q_low_cs`

The consumer benefit for low income consumers is `r cs_low`.

#### High Income

```{r High Income CS}

# Find Q at equilbrium -----

# 3 = 15.80343 - 2.730926e-05x
# 3 - 15.80343 = - 2.730926e-05x
# (3 - 15.80343) / - 2.730926e-05 = x

q_high_cs = (gas_price - demand_high_y)/demand_high_slope
  
# Low Income CS ------

cs_high = 0.5*(demand_high_y - gas_price)*q_high_cs

```

$x_{high}$ = (`r gas_price` - `r demand_high_y`)/`r demand_high_slope`

The quantity for the high income demand curve where the price is $`r gas_price` is `r q_high_cs`. 
  
`r cs_low` = 0.5 * (`r demand_high_y` - `r gas_price`) *`r q_high_cs`

The consumer benefit for high income consumers is `r cs_high`.

```{r Aggregate Benefit}

cs_agg = cs_low + cs_high
```

The aggregate benefit is `r cs_agg`.


## Question 3 - Effects from Gas Tax

#### a) The amount of gasoline produced and consumed. 


```{r Equilbrium Quantity after Tax}

gas_tax = 1.00

# Find new supply curve after tax - just add 1 to y-intercept?
supply_curve_tax = function(x){y = supply_slope*x + gas_tax}

# Find equilibrium after tax  ----

# Set supply and aggregate demand curves equal to each other to find Q
# --> y = (1/200,067x) + 1.00
# --> (1/200,067x) + 1.00 = 14.59968 - 1.932632e-05x
q_equil_tax = (demand_agg_y - gas_tax)/(supply_slope - demand_agg_slope)
```


$`r gas_tax` will be subtracted from every gallon purchased. 

The new supply curve is $y - 1 = (1/200,067)x$. Less gas would be produced and consumed. Setting this new supply curve equal to the aggregate demand curve, the new equilibrium quantity is `r q_equil_tax` gallons.

#### b) Gas price

```{r Gas Price after Tax}

gas_price_tax = supply_curve_tax(q_equil_tax)

```

The new gas price is `r round(gas_price_tax, 2)`/gallon at `r q_equil_tax` gallons.

#### c) Welfare of 'high' income consumers

```{r High Income CS after Tax}

# Find new Q for equil for high income after tax

# (1/200,067x) + 1.00 = 15.80343 - 2.730926e-05x
# x = 458,203

q_high_tax = (gas_tax - demand_high_y)/(demand_high_slope - supply_slope)

# Ask Haley about this math later ---
# 15.80343 - 2.730926e-05(458,203)
# y = 3.29024514022

# .5 * 458,203 * (15.80343 - 3.29024514022)
# = 2,866,789.42115288767

# Find consumer benefit ----

cs_high_tax = 0.5*(demand_high_y - gas_price_tax)*q_high_tax
```

`r q_high_tax` = (`r gas_tax` - `r demand_high_y`)/(`r demand_high_slope` - `r supply_slope`)

The quantity where P = `r round(gas_price_tax, 2)` is `r q_high_tax`

`r cs_high_tax` = 0.5 * (`r demand_high_y` - `r gas_price_tax`) * `r q_high_tax`

The welfare of high income customers after the tax is `r cs_high_tax`.

#### d) Welfare of 'low' income consumers

```{r Low Income CS after Tax}

# Find new Q for equil for low income after tax

# (1/200,067x) + 1.00 = 11.68548 - 6.611437e-05x
# x = 150,261

q_low_tax = (gas_tax - demand_low_y)/(demand_low_slope - supply_slope)

# Ask Haley about this math later ---
# 11.68548 - 6.611437e-05(150,261)
# y = 1.75106864943

# .5 * 150,261 * (11.68548 - 1.75106864943)
# = 746,377.291973999385

# Find consumer benefit ----

cs_low_tax = 0.5*(demand_low_y - gas_price_tax)*q_low_tax
```

`r q_low_tax` = (`r gas_tax` - `r demand_low_y`)/(`r demand_low_slope` - `r supply_slope`)

The quantity where P = `r round(gas_price_tax, 2)` is `r q_low_tax`

`r cs_low_tax` = 0.5 * (`r demand_low_y` - `r gas_price_tax`) * `r q_low_tax`

The welfare of low income customers after the tax is `r cs_low_tax`.

#### e) Welfare of gas producers

```{r PS after tax}

# Find Q on original supply curve at P = 1

# 3.795 = (1/200,067x) + 1.00
# x = 559187
q_ps_tax = (gas_price_tax - gas_tax)/supply_slope

# Find PS after tax

# integrate (1/200,067x) + 1.00 from 0 to 559187
# = 1,340,650


```
  
The welfare of gas consumers is $ ___.

#### f) Local environmental damage

A tax of $\$1.00$ doesn't cover all of local environmental damage, but it covers more than half of it, raising the tax to $\$2.00$.

#### g) Rest of world environmental damage

A tax of $\$1.00$ covers all of the world environmental damage and more. A socially optimum equilibirum is met at least with this externality. The MPC has captured the MEC value of this externality. The new supply curve with the tax is the MSC.

#### h) Total revenue generated by the tax

```{r Tax revenue}

# Haley's math -----

# y (new supply w/ tax) = 1/200,067x + 1
# y agg. = 14.59968 - 1.932632e-05x

# 14.59968 - 1.932632e-05x = 1/200,067x + 1
# x = 559,091
# y (new) = 3.7945
# y (old) = 2.7945

# tax revenue = 559,091

# Find the difference in P (3.79-1) multiply by q_equil_tax to get tax revenue

tax_revenue = (gas_price_tax - gas_tax)*q_equil_tax

```

The total revenue generated by the tax is `r tax_revenue`.

## Question 4

```{r Table of Welfare for Both Groups under Different Taxes}

# Create vector for a range of different gas taxes
gas_tax_vector = c(0, 1, 2, 3, 4, 5)

# Create function for high income CS
#cs_high_tax_function = function(t) {
  #total_cs = 0.5*q*(p - gas_tax_vector) + (p - gas_tax_vector)*q
#}

# Create function for low income CS
#cs_low_tax_function = function(t) {
  #total_cs = 0.5*q*(p - gas_tax_vector) - (local_externality*___)
#}

# Create function for PS
#ps_tax_function = 0.5*q*(p - gas_tax_vector)


```

#### a) overall welfare of 'High' income consumers

```{r}

# Haley's math ---

# welfare before tax revenue = 4,374,390
# gas comsumed = 458,203
# % = 458,203/608,464 = 75%

# 'High' income earners get 75% of tax reveneue, which is 419318.25

# Total welfare = 4,793,708.3

 # - it they only have to pay world externality ($.50) 
 # - .50$ tax
  
#15.80343 - 2.730926e-05x = 1/200,067x + .50
#x = 473,679
#integrate 15.80343 - 2.730926e-05x from 0 to 473,679
#= 4,422,040
```



#### b) overall welfare of 'Low' income consumers

```{r}

# Haley's math ---

# welfare before tax = 1,009,490
# gas consumed = 150,261
# % = 150,261/608,464 = 25%

# 'Low' income earners get 25% of tax reveneue, which is 139,772.75

# Total welfare = 1,149,262.8
```


The low income customers have to pay a higher tax because they have greater MECs. We assume that they will cover both the local externality and the ROW externality.

```{r Calculating global externality}

global_externality = local_externality + row_externality

# Haley's math ---
# 11.68548 - 6.611437e-05x = 1/200,067x + 2
# x = 136,199
# integrate 11.68548 - 6.611437e-05x from 0 to 136,199
# = 978,334
```

Global externality = $\$1.50 (local)$ + $\$0.50 (ROW)$ = $\$2.00$

They will need to pay a $`r global_externality` tax.
  

Maybe the ideal tax is $\$1.25$ because $2 + .50 = 2.50$ which split between two groups is $1.25$. 

#### c) gas producers

```{r}

# y (supply) = (1/200,067x) + 1 
# y (aggregate demand) = 14.59968 - 1.932632e-05x

# (1/200,067x) + 1 = 14.59968 - 1.932632e-05x
# x = 559,091
# integrate (1/200,067x) + 1 from 0 to 559,091
# = 1,340,300
```


## Question 5 - EV Technology

**Note:** For the following calculations, we divided the y-intercept of each demand curve by half.

```{r New Demand Curves with Electric Vehicles}

# Divide y-intercepts by 1/2

# New low income curve:
demand_low_ev = function(q){(11.7 - (6.61*10^{-5})*q)/2}

# New high income curve:
demand_high_ev = function(y){y = demand_high_ev_y - demand_high_slope*x}

```

#### a) gas consumption by 'High' income consumers

```{r Gas Consumption by High Income w/ EV}

# Calculate Q with new demand curve with original supply curve

# Haley's math ---
# old: y = 15.80343 - 0.00002730926x
# 15.80343 - 0.00002730926x = 1/200,067x
# x = 489,155
# new: y = (15.80343/2) - 0.00002730926x
# (15.80343/2) - 0.00002730926x = 1/200,067x
# x = 244,578

# Find new y-intercept
demand_high_ev_y = demand_high_y/2

# Find new equilibrium quantity
q_high_ev = demand_high_ev_y/(supply_slope - demand_high_slope)

# Calculate percentage decrease
q_high_percentage = q_high_ev/q_high_cs*100

```

The new consumption by high income consumers is `r q_high_ev` gallons. Consumption decreases about `r round(q_high_percentage, 1)`%

#### b) gas consumption by 'Low' income consumers

```{r Gas Consumption by Low Income w/ EV}

# Calculate Q with new demand curve with original supply curve

# Haley's math ---
# old: y = 11.68548 - 0.00006611437x
# 11.68548 - 0.00006611437x = 1/200,067x
# x = 164,323
# new: y = (11.68548/2) - 0.00006611437x
# (11.68548/2) - 0.00006611437x = 1/200,067x
# x = 82,161.7

# Find new y-intercept
demand_low_ev_y = demand_low_y/2

# Find new equilibrium quantity
q_low_ev = demand_low_ev_y/(supply_slope - demand_low_slope)

# Calculate percentage decrease
q_low_percentage = q_low_ev/q_low_cs*100

```

The new consumption by high income consumers is `r q_low_ev` gallons. Consumption decreases about `r round(q_low_percentage, 1)`%

#### c) gas price

```{r Gas Price after EV}

# Haley's math ---

#old agg.: 14.59968 - 1.932632e-05x
#14.59968 - 1.932632e-05x = 1/200,067x
#x = 600,201
#new agg.: (14.59968/2) - 1.932632e-05x
#(14.59968/2) - 1.932632e-05x = 1/200,067x
#x = 300,101
#new equilibrium = 300,101 gallons at $1.49 /gallon

# Find new aggregate demand curve ----

# Find new y-intercept for original aggregate demand curve
demand_agg_ev_y = demand_agg_y/2

# Create new function for aggregate demand curve
demand_agg_ev = function(x){y = demand_agg_ev_y + demand_agg_slope*x}

# Find a Q for new equilibrium ----

# Set new aggregate demand curve equal to original supply curve
q_equil_ev = demand_agg_ev_y/(supply_slope - demand_agg_slope)

# Find the new P for new equilibrum
p_equil_ev = demand_agg_ev(q_equil_ev)

```

The new gas price is $`r p_equil_ev`.

#### d) local environmental damage from gasoline

$.5 * 1.50 * 300,101 = 225,075.75$

#### e) rest of world environmental damage from gasoline

$.5 * .50 * 300,101 = 75,025.25$


## Question 6

```{r Socially Optimal Tax}

# Haley's math ---
#new quantity with new technology = 300,101
#old supply: y = 1/200,067x
#new supply with tax: y = (1/200,067x) + $\tau$
#solve for $\tau$
#find P value from demand curve: 14.59968 - 1.932632e-05(300,101) = 8.79983204168
#8.79983204168 = (1/200,067(300,101)) + $\tau$
#$\tau$ = 7.29982954252
#new supply with tax: y = (1/200,067x) + 7.29982954252

# Write new supply equation with tax
supply_curve_optimal_tax = function(x, y, t){
  y = supply_slope*x + t
}

# Find P from demand curve using the equilbrium quantity from the EV calculations
p_optimal_tax = demand_agg_y + demand_agg_slope*q_equil_ev

# Find t by plugging new price back into the supply curve plus tax
tax_optimal = p_optimal_tax - supply_slope*q_equil_ev



```

$\tau$ = `r round(tax_optimal, 2)`

**New supply curve with optimal tax:** y = `r supply_slope`x + `r round(tax_optimal, 2)`

A tax of $`r round(tax_optimal, 2)` makes the local environmental quality equal between the gas tax situation and the electric car situation.


